The Astropy Project

### 2017-10-20 main.tex
Update on Overleaf.
Some more inline comments

@@

Lupton et al. (2004) describe an “optimal” algorithm for producing red-green- blue composite images from three separate high-dynamic range arrays. This method is implemented in make_lupton_rgb as a convenience wraper function and an associated set of classes to provide alternate scalings. The SDSS SkyServer color images were made using a variation on this technique.

@@

% \section{State of the Ecosystem}
% Commenting out unless a clear statement is added

@@

\section{The future of the Astropy project}
\label{sec:future}
\inlinecomment{PLL}{In addition to PY3, add some killer features that we plan to implement for 3.0 and beyond?}
\subsection{Roadmap for \python 3 only support}

>>>>

The package also provides the a histogram function, which is a generalization of \package{matplotlib}’s histogram function, to allow for more flexible specification of histogram bins.  The function provides several methods of automatically tuning the histogram bin size. It has a syntax identical \package{matplotlib}’s histogram function, with the exception of the bins parameter, which allows specification of one of four different methods for automatic bin selection.

@@

Lupton et al. (2004) describe an “optimal” algorithm for producing red-green- blue composite images from three separate high-dynamic range arrays. The \package{visualization} package provies a convenience function to create such an image.  It also includes an associated set of classes to provide alternate scalings.  The SDSS SkyServer color images were made using a variation on this technique.

@@

\inlinecomment{BMS}{What about pytest-astropy, should we inlude it here, or
  for the future section?}
% \section{State of the Ecosystem}
% Commenting out unless a clear statement is added

@@

\section{The future of the Astropy project}
\label{sec:future}
\inlinecomment{PLL}{In addition to PY3, add some killer features that we
  plan to implement for 3.0 and beyond?}
\inlinecomment{BMS}{Some killer features we already know about to definitely
have may be mentioned here. e.g. functionality of astropy-healpix? or the
performance/speedup focus of the 3.1 release?}
\inlinecomment{BMS}{should we mention the refactored infra here?
  e.g. pytest-astropy and sphinx-astropy?}
\subsection{Roadmap for \python 3 only support}
